\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.50in,top=0.5in,right=0.50in,bottom=0.5in]{geometry} % Document margins
\usepackage{amsmath}

%----------------------------------------------------------------------------------------
%   NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\name{Cat Ngo} % Your name at the top
\address{\textsf{6461 Telford Ave, Apt 1008, Burnaby BC, 5H 0B7}}
\address{\textsf{cathan.ngo@gmail.com} -- \textsf{424.603.1376}}
\address{\textsf{github.com/catngo}}

\begin{document}

\begin{rSection}{EXPERIENCE}

    \begin{rSubsection}{Senior Software Development Engineer -- Remitly}{10/10/24 -- Now}{Authentication and Trust Experience Team}{}
        \item Implemented and tested Compliance data  integration when Remitly integrates with a new vendor (Hummingbird) to handle STAR and AML investigation
        \item Conducted deep dives on legacy Risk dependencies to unblock Remitly's integration with the new Okta's Auth0 authentication flow
        \item Designed and implemented a new workflow to handle automatic transaction cancellation and customer's notification to replace a legacy workers queue
    \end{rSubsection}


    \begin{rSubsection}{Software Development Engineer, II -- Remitly}{10/01/21 -- 7/23/24}{Fraud Prevention/Remittance Risk Orchestration Team}{}
        \item Designed and implemented the Enhanced Due Diligence (EDD) framework that relies on a customer’s risk rating. EDD allowed Remitly to removes the legacy Tier Limits framework that presented high friction to customers who wanted to send high volume. When rolled out, EDD increased the net send amount from customers by 6 to 8\%.
        \item Partnered with Fraud analysts to deliver necessary data to stop emergent fraud attacks.
        \item Designed and implemented an event-driven architecture (leveraging AWS SQS and Goroutine) to consume and write customer’s data into our graph database (AWS Neptune) as part of a company-wide effort to decouple from reading legacy RDS instance.
        \item Implemented the user experience in Typescript and React-Native that allows customers to directly call Customer Service from our app when their transaction has been in review for longer than two hours, leading to a 13\% increase in transaction completion rate.
        \item Implemented and released the functionality (written in PHP), allowing Customer Service agents to temporarily disable Multi-Factor Authentication (MFA), making MFA not being permanently disabled for the customer and increasing our customer’s account security and protecting them from an Account Takeover attack.
    \end{rSubsection}
    
    \begin{rSubsection}{Software Development Engineer, I -- Remitly}{02/16/21 -- 09/30/21}{Fraud Prevention Team}{}
        \item Optimized a data extraction job in Scala by using a Spark custom incremental extractor, reducing the daily run time from 12 hours to less than 1 hour.
        \item Implemented Prometheus alarms to support program managers and analysts in detecting early warnings of fraudulent activity, saving an estimated \$400k of losses in 2021.
        \item Migrated Fraud systems to Kubernetes and AWS EKS cluster, leading to cost reduction (saving an estimated \$20k per year) and better scalability of our systems as well as complying with Security and Compliance policy.
        \item Mentored a Software Engineer Intern and supported him in ramping up and delivering impactful project, leading to him accepting the offer to return to the team as a full-time engineer.
    \end{rSubsection}
    
    \begin{rSubsection}{Software Development Engineer, I -- Remitly}{07/21/20 -- 02/15/21}{Customer Transaction Accounting Processing Team}{}
        \item Optimized a Go worker process writing disbursement data by using a memory profiler (pprof) and reduced the runtime by 7 hours as well as making the process more resilient to failures.
        \item Implemented and wrote rigourous integration testing for the improved loss logic state machine (written in Go), which processes 24 million financial events every day to accurately identify accounting loss.
        \item Implemented functionality to emit events indicating accounting loss by integrating a Go service with existing Flink-SQS event pipeline.
        \item Documented and diagrammed the complex state machine for identifying accounting loss using LucidChart and hosted knowledge-sharing sessions with the team.
    \end{rSubsection}
    \pagebreak
    \begin{rSubsection}{Software Development Engineer, Summer Intern -- Remitly}{06/17/19 -- 08/30/19}{Pricing Team}{}
        \item Implemented API endpoint in Java to fetch history of pricing rules and designed the UI using Javascript and Node to reference that history, leading to greater ease-of-use and productivity for pricing analysts to set offered exchange rates.
        \item Implemented dimensioned scrapers in Python that retrieved pricing data from competitor, increasing data processing throughput by 5 times as measured by the number of queries per day.
        \item Redesigned the representation of pricing quote to allow for better readability of the economics logic behind a quote.
        \item Developed AWS RDS relational database that persisted transaction quotes and integrated it with PHP platform codebase, allowing for after-the-fact access of the pricing quotes of enqueued transactions.
    \end{rSubsection}
\end{rSection}

\begin{rSection}{EDUCATION}
{\bf Harvey Mudd College} \hfill {\em Graduated May 2020} \\
{\em Joint Computer Science and Mathematics (B.S.)}\hfill {\em Major GPA 3.835} \\
\end{rSection}
\begin{rSection}{SKILLS}

\textbf{Programming Languages:} Go, Kotlin, Scala, Python, Java, C++, SQL, Typescript, JavaScript, PHP, Haskell, Prolog, Racket, R, HTML/CSS  \\
\textbf{Software Libraries:} AWS SDK, Spark, Pprof, JDBI, Lombok, Jackson, Numpy, Scikit-Learn, React  \\
\textbf{Utilities:} AWS (SQS, RDS, DynamoDB, Redshift, S3, Flink), Prometheus, Jenkins, Docker, Gradle, Maven, \LaTeX, Kubernetes, Git, Tecton  
\end{rSection}
\end{document}
